Verifying Demonstrations

### 2018-02-19 paper/DB-anon-cred.tex
DBS: improves protocol fig, adds analysis

    \(R_0\gets g^{\rho_0}, R_1\gets g^{\rho_1}\)
    & \(\ProtoSendRight{R}\)
    & \\

    % null
    & \(\ProtoSendLeft{c}\)
    & \(c_0\rgets \bin^k, c_1\rgets \bin^k\) \\

@@

%    % null
%    &
%    & Random delay \\

@@

    \(r_i\gets s_{b_i}[i]\)
    & \(\ProtoSendRight{r_i}\)
    & \\

@@

The intuition behind the protocol security is as follows.
The random delay in the \ac{DB} phase is important to prevent distance fraud.
Otherwise \iac{DBDF} prover could just send all bits timed to the expected 
round-trip time without waiting for the challenges.

Concerning Mafia fraud, the \ac{DBMF} adversary does not know which challenge 
the verifier will use, thus there is a \(1/2\) probability that the \ac{DBMF} 
adversary will guess it correctly.
The prover will only provide one of the responses: even if the adversary re-runs 
the protocol with the same challenges, the randomly chosen \(\rho_0, \rho_1\) 
will have changed --- which thus yields another \(R_b\) in the end of the 
protocol.

>>>>

    \(R_0\gets g^{\rho_0}, R_1\gets g^{\rho_1}\)
    & \(\ProtoSendRight{R_0, R_1}\)
    &
    \\

    % null
    & \(\ProtoSendLeft{c_0, c_1}\)
    & \(c_0\rgets \bin^k, c_1\rgets \bin^k\)
    \\

@@

%    % null
%    &
%    & Random delay
%    \\

@@

    \(r_i\gets s_{b_i}[i]\)
    & \(\ProtoSendRight{r_i}\)
    & Record \(\Delta t_i\)
    \\

@@

The intuition behind the protocol security is as follows.
To achieve malicious-verifier zero-knowledge we must choose \(k\) 
logarithmically in the security parameter \(\lambda\) and repeat the protocol 
until the knowledge error is small enough.
This will actually also decrease the success probability of \iac{DBMF} adversary 
in the \ac{DB} step.
The \ac{DBMF} adversary does not know which challenge the verifier will use, 
thus there is a \(1/2\) probability that the \ac{DBMF} adversary will guess it 
correctly.
The prover will only provide one of the responses: even if the adversary re-runs 
the protocol with the same challenges, the randomly chosen \(\rho_0, \rho_1\) 
will have changed --- which thus yields another \(R_b\) in the end of the 
protocol.
By repeating the protocol we can bring this probability down as much as desired.

The random delay in the \ac{DB} phase is important to prevent distance fraud.
Otherwise \iac{DBDF} prover could just send all bits timed to the expected 
round-trip time without waiting for the challenges.
On the other hand, these delays must not be long enough to allow the \ac{DBMF} 
adversary to buffer the responses from the prover.
